New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2023-02-08 paper/paper.Rmd
added plotly to rgl part

\textcolor{blue}{Within R, the natural implementation for an interactive interface would use} `shiny` [@shinym] with `plotly` [@plotly] drawing. However, the `plotly` package is designed to add to `ggplot2` [@ggplot2] graphics, not to be a programmable interactive graphics system. It lacks the capability to implement the primary tool needed for a manual tour, which is the tracking of the cursor position in small increments. In theory, the historical `locator()` function of base R should provide the necessary capability, but its behavior is not consistent between graphical devices. The cursor position control is possible with `rgl` [@rgl] but this package is focused on 3D, not the arbitrary dimension of tours. The level of interactivity would have been possible with the `cranvas` system [@cranvas] or `rJava` [@rJava] but neither has a graphics toolkit that currently operates across platforms.  What we have chosen to do is to use the interactivity of Mathematica to experiment, and to implement the resulting ideas as an animation in the `tourr` [@tourr] package. There is hope that better interactivity will be available for R soon, perhaps in javascript [e.g. @langevitour, @detourr], which might allow for the experimentation to develop new techniques.

\textcolor{red}{plotly does 3D graphs that can be dragged as well, maybe need to clarify further? Are there any references that document shortcomings? Maybe this paragraph should be a subsection?}

>>>>

\textcolor{blue}{Within R, the natural implementation for an interactive interface would use} `shiny` [@shinym] with `plotly` [@plotly] drawing. However, the `plotly` package is designed to add to `ggplot2` [@ggplot2] graphics, not to be a programmable interactive graphics system. It lacks the capability to implement the primary tool needed for a manual tour, which is the tracking of the cursor position in small increments. In theory, the historical `locator()` function of base R should provide the necessary capability, but its behavior is not consistent between graphical devices. The cursor position control is possible for 3D plots with `rgl` [@rgl] and `plotly` but these not the arbitrary dimension needed for tours. The level of interactivity would have been possible with the `cranvas` system [@cranvas] or `rJava` [@rJava] but neither has a graphics toolkit that currently operates across platforms.  What we have chosen to do is to use the interactivity of Mathematica to experiment, and to implement the resulting ideas as an animation in the `tourr` [@tourr] package. There is hope that better interactivity will be available for R soon, perhaps in javascript [e.g. @langevitour, @detourr], which might allow for the experimentation to develop new techniques.

### 2023-02-08 paper/paper.tex
added plotly to rgl part

\textcolor{blue}{Within R, the natural implementation for an interactive interface would use}
\texttt{shiny} \citep{shinym} with \texttt{plotly} \citep{plotly}
drawing. However, the \texttt{plotly} package is designed to add to
\texttt{ggplot2} \citep{ggplot2} graphics, not to be a programmable
interactive graphics system. It lacks the capability to implement the
primary tool needed for a manual tour, which is the tracking of the
cursor position in small increments. In theory, the historical
\texttt{locator()} function of base R should provide the necessary
capability, but its behavior is not consistent between graphical
devices. The cursor position control is possible with \texttt{rgl}
\citep{rgl} but this package is focused on 3D, not the arbitrary
dimension of tours. The level of interactivity would have been possible
with the \texttt{cranvas} system \citep{cranvas} or \texttt{rJava}
\citep{rJava} but neither has a graphics toolkit that currently operates
across platforms. What we have chosen to do is to use the interactivity
of Mathematica to experiment, and to implement the resulting ideas as an
animation in the \texttt{tourr} \citep{tourr} package. There is hope
that better interactivity will be available for R soon, perhaps in
javascript \citep[e.g.][\citet{detourr}]{langevitour}, which might allow
for the experimentation to develop new techniques.

\textcolor{red}{plotly does 3D graphs that can be dragged as well, maybe need to clarify further? Are there any references that document shortcomings? Maybe this paragraph should be a subsection?}

>>>>

\textcolor{blue}{Within R, the natural implementation for an interactive interface would use}
\texttt{shiny} \citep{shinym} with \texttt{plotly} \citep{plotly}
drawing. However, the \texttt{plotly} package is designed to add to
\texttt{ggplot2} \citep{ggplot2} graphics, not to be a programmable
interactive graphics system. It lacks the capability to implement the
primary tool needed for a manual tour, which is the tracking of the
cursor position in small increments. In theory, the historical
\texttt{locator()} function of base R should provide the necessary
capability, but its behavior is not consistent between graphical
devices. The cursor position control is possible for 3D plots with
\texttt{rgl} \citep{rgl} and \texttt{plotly} but these not the arbitrary
dimension needed for tours. The level of interactivity would have been
possible with the \texttt{cranvas} system \citep{cranvas} or
\texttt{rJava} \citep{rJava} but neither has a graphics toolkit that
currently operates across platforms. What we have chosen to do is to use
the interactivity of Mathematica to experiment, and to implement the
resulting ideas as an animation in the \texttt{tourr} \citep{tourr}
package. There is hope that better interactivity will be available for R
soon, perhaps in javascript \citep[e.g.][\citet{detourr}]{langevitour},
which might allow for the experimentation to develop new techniques.
